### 2020-04-28 Paper/paper.tex
minor paper changes

% AUTHOR NAMES GOES HERE
\author{
\IEEEauthorblockN{Shawn Mace}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
sdm2w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Derrick Reckers}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
dmr3p@mtmail.mtsu.edu}\\
\and
\IEEEauthorblockN{Aric Moilanen}
\IEEEauthorblockA{\textit{Department of Physics and Astronomy} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
atm4w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Jarrett Shaver}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
Jarrett.shaver@gmail.com}\\
\and
\IEEEauthorblockN{Matthew Ogden}
\IEEEauthorblockA{\textit{Computational Science, PhD Program} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
mbo2d@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Devon Wilson}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
email address}\\
}
\maketitle

@@

When two galaxies merge, it causes a drastic change in the
evolution of the resulting galaxy. Understanding ongoing
collisions in the night sky, will aid scientists in their exploration
to uncover more about merging galaxies. Unfortunately,
information such as orbital velocities, orientations, and mass-ratios between the two galaxies cannot be obtained from
observation alone.

@@

This project takes data from galactic models and associated
human fitness scores, with the goal to develop several Neural
Network Tools that help scientists better understand this
data, and develop a machine fitness score that matches the
human fitness score. By having theses tools, scientists can
quicken the search to find those well-fitting models, explore
the galactic model parameter space, and hopefully find the
true dynamic parameters for observable galaxy collisions.

@@

In our second net, we attempted to utilize the superior image recognition characteristics of a convolutional neural net. As a base, we used the convolutional neural net used on the cat problem in OLA 6 \cite{phillips}. In this net, there are two 2D convolution layers that feed into a pooling layerThe main changes made were to kernel size and the final dense layer. There are two 2D convolution layers use a standard ReLu activation function, which are then followed by pooling and dropout layer. It is the passed into a flattening layer and a single dense layer, still with a ReLu activation function, before passing though a final dropout layer and into the final dense layer. The main changes we made to this architecture from OLA 6 were in terms of kernel size, unit size of the dense and convolution layers, and the setup of the final dense layer.

@@

Shown in Fig. \ref{fig:SingleModelLoss} is the training and validation loss history over 120 epochs. At the end of 120 epochs, the model had decreased to a MSE loss of 0.012 for the training data and 0.019 for the validation data. We can also plainly see the overfitting the plagued both of our neural nets, regardless of the hyperparameter tuning we performed to try to remove it.

@@

Fig. \ref{fig:SinglePredictedVAct} shows the values predicted by the single layer net on the 90 testing images verus their human scores. We see a linear correlation between the two, which is what we hoped to observe. A perfect linear correlation would have meant that the model was guessing exactly the same as the human score.

>>>>

% AUTHOR NAMES GOES HERE
\author{
\IEEEauthorblockN{Shawn Mace}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
sdm2w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Derrick Reckers}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
dmr3p@mtmail.mtsu.edu}\\
\and
\IEEEauthorblockN{Aric Moilanen}
\IEEEauthorblockA{\textit{Department of Physics and Astronomy} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
atm4w@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Jarrett Shaver}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
Jarrett.shaver@gmail.com}\\
\and
\IEEEauthorblockN{Matthew Ogden}
\IEEEauthorblockA{\textit{Computational Science, PhD Program} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
mbo2d@mtmail.mtsu.edu}\\
\IEEEauthorblockN{Devon Wilson}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Middle Tennessee State University}\\
Murfreesboro, United States \\
djw4s@mtmail.mtsu.edu}\\
}
\maketitle

@@

When two galaxies merge, it causes a drastic change in the
evolution of the resulting galaxy. Understanding ongoing
collisions in the night sky will aid scientists in their exploration
to uncover more about merging galaxies. Unfortunately,
information such as orbital velocities, orientations, and mass-ratios between the two galaxies cannot be obtained from
observation alone.

@@

This project takes data from galactic models and associated
human fitness scores, with the goal to develop both a single layer 
neural net and a convolutional neural net that will help scientists better understand this
data. These two nets will be used to produce a machine fitness score for each model image
that we hope will closely match its respective human fitness score. We will compare these two networks based on how well they were able to match human scores with their predictions.
By having theses tools like these neural networks, scientists can
quicken the search to find those well-fitting models, explore
the galactic model parameter space, and hopefully find the
true dynamic parameters for observable galaxy collisions.

@@

In our second net, we attempted to utilize the superior image recognition characteristics of a convolutional neural net. As a base, we used the convolutional neural net used on the cat problem in OLA 6 \cite{phillips}. In this net, there are two 2D convolution layers that feed into a pooling layer.  The main changes made were to kernel size and the final dense layer. There are two 2D convolution layers that use a standard ReLu activation function, which are then followed by pooling and dropout layer. It is then passed into a flattening layer and a single dense layer, still with a ReLu activation function, before passing though a final dropout layer and into the final dense layer. The main changes we made to this architecture from OLA 6 were in terms of kernel size, unit size of the dense and convolution layers, and the setup of the final dense layer.

@@

Shown in Fig. \ref{fig:SingleModelLoss} is the training and validation loss history over 120 epochs. At the end of 120 epochs, the model had decreased to a MSE loss of 0.012 for the training data and 0.019 for the validation data. We can also plainly see the overfitting that plagued both of our neural nets, regardless of the hyperparameter tuning we performed to try to remove it.

@@

Fig. \ref{fig:SinglePredictedVAct} shows the values predicted by the single layer net on the 90 testing images verus their generated scores. We see a linear correlation between the two, which is what we hoped to observe. A perfect linear correlation would have meant that the model was guessing exactly the same as the human score.
